---
title: "HW4"
author: "Zimeng Liu"
date: "2022-10-13"
output: word_document
---
Q1.
Good and Standard
```{r}
library(dplyr)
creditScore <- read.csv('C:\\Users\\Zimeng\\OneDrive - Dickinson College\\Desktop\\Dickinson\\7th\\DATA 300\\HW\\credit_score.csv')
table(creditScore$Credit_Score)
Poor_Good <- filter(creditScore, creditScore$Credit_Score %in% c("Good","Poor"))
Poor_Good$Credit_Score <- factor(Poor_Good$Credit_Score, levels = c("Good","Poor"), labels=c(0,1))
# levels(Poor_Good$Credit_Score)
# View(Poor_Good)
```
Q2.
I decide to include outstanding debt, amount invested monthly, credit utilization ratio, delay from due date, and number of bank account.
```{r}
Poor_Good <- na.omit(Poor_Good)

is.numeric(Poor_Good$Outstanding_Debt)
Poor_Good$Outstanding_Debt <- as.numeric(Poor_Good$Outstanding_Debt)
is.numeric(Poor_Good$Outstanding_Debt)

is.numeric(Poor_Good$Amount_invested_monthly)
Poor_Good$Amount_invested_monthly <- as.numeric(Poor_Good$Amount_invested_monthly)
is.numeric(Poor_Good$Amount_invested_monthly)

is.numeric(Poor_Good$Credit_Utilization_Ratio)

is.numeric(Poor_Good$Num_Credit_Inquiries)

is.numeric(Poor_Good$Delay_from_due_date)

is.numeric(Poor_Good$Num_Bank_Accounts)

Poor_Good <- na.omit(Poor_Good)
```
Q3.
In both train set and validation set, the distribution of Good class is about 37% and that of Poor class is about 63%.
```{r}
set.seed(111)
sample <- sample(c(TRUE, FALSE), nrow(Poor_Good), replace=TRUE, prob=c(0.7,0.3))
train <- Poor_Good[sample, ]
validation <- Poor_Good[!sample, ]

prop.table(table(train$Credit_Score))
prop.table(table(validation$Credit_Score))
```
Q4.
```{r}
options(scipen=200)
model1 <- glm(as.factor(Credit_Score) ~ Outstanding_Debt + Amount_invested_monthly + Credit_Utilization_Ratio + Num_Credit_Inquiries + Delay_from_due_date + Num_Bank_Accounts, family = "binomial", data = train)
summary(model1)
```
Q5.
For Outstanding_Debt, the coefficient means that every unit change in Outstanding_Debt, the log-odds change by 0.00120700.

Q6.
The worst mistake for a bank is to take a client with a poor credit score as a client with a good credit score. Thus, I choose to use False omission rate (FOR) to evaluate this model. FN/PN = 3323/(3323+1307) = 0.718.
```{r}
pred1 <- predict(model1, validation, type = "response")
summary(pred1)
pred1_class <- ifelse(pred1 > 0.63, 1, 0)
table(validation$Credit_Score, pred1_class)
```
Q7.
My LDA function actually ran pretty fast.
```{r}
library(MASS)
model2 <- lda(as.factor(Credit_Score) ~ Outstanding_Debt + Amount_invested_monthly + 
    Credit_Utilization_Ratio + Num_Credit_Inquiries + Delay_from_due_date + Num_Bank_Accounts, data = train)
model2
pred2 <- predict(model2, validation)
```
Q8.
```{r}
model3 <- qda(as.factor(Credit_Score) ~ Outstanding_Debt + Amount_invested_monthly + 
    Credit_Utilization_Ratio + Num_Credit_Inquiries + Delay_from_due_date + Num_Bank_Accounts, data = train)
model3
pred3 <- predict(model3, validation)
```
Q9.
```{r}
library(pROC)
plot(roc(validation$Credit_Score, pred1),col = "yellow")
plot(roc(validation$Credit_Score, pred2$posterior[,-1], add=TRUE), col = "blue")
plot(roc(validation$Credit_Score, pred3$posterior[,-1], add=TRUE), col = "green")
```
Q10.
Thus, I choose to use False omission rate (FOR) to evaluate this model. FN/PN = 3322/(3322+1307) = 0.718.
```{r}
thre <- seq(0.1, 0.9, 0.1)
forList <- 0

for (i in thre){
  pred_class <- ifelse(pred1 > i, 1, 0)
  confu <- table(validation$Credit_Score, pred_class)
  false_omission_rate <- confu[1,1]/length(which(validation$Credit_Score == 0)) 
  forList <- c(forList, false_omission_rate)
  print(confu)
}

length(thre)
length(forList)
plot(thre,forList[-1])
```
